
\element{class11}{
  \begin{question}{c11q1}
    In the Bitcoin scripting language, what is a common operation used for creating multi-signature transactions?
    \begin{choices}
      \correctchoice{CHECKMULTISIG}
      \wrongchoice{CHECKLOCKTIMEVERIFY}
      \wrongchoice{CHECKSEQUENCEVERIFY}
      \wrongchoice{OP_RETURN}
    \end{choices}
  \end{question}
}

\element{extra}{
  \begin{question}{c11q2}
    Which type of script allows the spending of funds only if a certain condition is met within a specified time frame?
    \begin{choices}
      \correctchoice{Timelock script}
      \wrongchoice{Hashlock script}
      \wrongchoice{Multisig script}
      \wrongchoice{Pay-to-Public-Key-Hash (P2PKH) script}
    \end{choices}
  \end{question}
}

\element{extra}{
  \begin{question}{c11q3}
    In Ethereum, what is the scripting language used for developing smart contracts?
    \begin{choiceshoriz}[o]
      \wrongchoice{C++}
      \wrongchoice{Python}
      \wrongchoice{Java}
      \correctchoice{Solidity}
    \end{choiceshoriz}
  \end{question}
}


\element{extra}{
  \begin{question}{c11q4}
     What is the primary reason for the flexibility of scripting languages in blockchain?
    \begin{choices}
      \wrongchoice{Increased security}
      \wrongchoice{Interoperability with traditional databases}
      \correctchoice{Customization of transaction logic}
      \wrongchoice{Faster transaction processing}
    \end{choices}
  \end{question}
}

\element{class11}{
  \begin{question}{c11q5}
    In the anatomy of a blockchain transaction, what is the transaction output responsible for?
    \begin{choices}
      \wrongchoice{Storing the sender's public key}
      \wrongchoice{Identifying the transaction ID}
      \correctchoice{Containing the recipient's address and amount}
      \wrongchoice{Holding the digital signature}
    \end{choices}
  \end{question}
}

\element{class11}{
  \begin{question}{c11q6}
    In a multisig locking script, what condition must be met to spend the funds?
    \begin{choices}
      \wrongchoice{A specific time window}
      \correctchoice{ Multiple private key signatures}
      \wrongchoice{A matching transaction ID}
      \wrongchoice{An OP_RETURN code}
    \end{choices}
  \end{question}
}

\element{class11}{
  \begin{question}{c11q7}
	In the context of public key cryptography, what is the primary role of the private key?
    \begin{choices}
      \wrongchoice{Encrypting data}
      \wrongchoice{  Verifying signatures}
      \correctchoice{Decrypting data}
      \wrongchoice{Generating public keys}
    \end{choices}
  \end{question}
}

\element{class11}{
  \begin{question}{c11q8}
    What information is included in the transaction output script of a Pay to Public Key (P2PK) transaction?
    \begin{choices}
      \wrongchoice{Recipient's public key hash}
      \correctchoice{Recipient's full public key}
      \wrongchoice{ Sender's private key}
      \wrongchoice{Transaction ID}
    \end{choices}
  \end{question}
}


