\element{class4}{
  \begin{question}{c4q1}
   What does a transaction look like in a blockchain?
    \begin{choices}
      \wrongchoice{Encrypted message}
      \wrongchoice{Smart contract}
      \wrongchoice{Hashed block}
      \correctchoice{Signed data packet }
    \end{choices}
  \end{question}
}

\element{class4}{
  \begin{question}{c4q2}
   Hash identifying each block in the blockchain is generated using which of the following cryptographic algorithm?
    \begin{choices}
      \wrongchoice{SHA128}
      \correctchoice{SHA256}
      \wrongchoice{Both of them}
      \wrongchoice{None of them}
    \end{choices}
  \end{question}
}

\element{class4}{
  \begin{question}{c4q3}
  What is the primary purpose of voting in a decentralized network or consensus mechanism?
    \begin{choices}
      \wrongchoice{Establishing a hierarchical structure among nodes}
      \wrongchoice{Verifying user identities in the network}
      \correctchoice{Reaching agreement on transactions and blocks}
      \wrongchoice{Assigning unique identifiers to nodes}
    \end{choices}
  \end{question}
}

\element{class4}{
  \begin{question}{c4q4}
   What is the name of the first block in a blockchain?
    \begin{choices}
      \correctchoice{Genesis block}
      \wrongchoice{Origin block}
      \wrongchoice{Block one}
      \wrongchoice{None of the above}
    \end{choices}
  \end{question}
}


\element{class4}{
  \begin{question}{c4q5}
   How is state maintained in a blockchain?
    \begin{choices}
      \wrongchoice{Centralized database}
      \correctchoice{Distributed ledger}
      \wrongchoice{Peer-to-peer network}
      \wrongchoice{Cloud storage}
    \end{choices}
  \end{question}
}



\element{class4}{
  \begin{question}{c4q6}
 What is a "consensus algorithm," and why is it important for block validation?
    \begin{choices}
      \correctchoice{It's a way to achieve unanimous decisions; it ensures agreement on the state of the blockchain.}
      \wrongchoice{It's a method for encrypting transactions; it secures data in the block.}
      \wrongchoice{It's a measure of a miner's credibility; it influences block rewards.}
      \wrongchoice{It's a timestamping mechanism; it organizes transactions in chronological order.}
    \end{choices}
  \end{question}
}

\element{class4}{
  \begin{question}{c4q7}
   How does a blockchain network ensure that a block is valid before adding it to the chain?
    \begin{choices}
      \wrongchoice{Through decentralized voting}
      \wrongchoice{By performing complex mathematical calculations}
      \correctchoice{Through consensus among a majority of nodes}
      \wrongchoice{By trusting the miner's reputation}
    \end{choices}
  \end{question}
}
