\element{class6}{
  \begin{question}{c6q1}
   What is the incentive for miners in a blockchain network?
    \begin{choices}
      \correctchoice{Transaction fees}
      \wrongchoice{Puzzle difficulty}
      \wrongchoice{Block size}
      \wrongchoice{Network latency}
    \end{choices}
  \end{question}
}

\element{class6}{
  \begin{question}{c6q2}
   How does the blockchain network adjust the difficulty of cryptographic puzzles for miners?
    \begin{choices}
      \wrongchoice{Randomly}
      \wrongchoice{Every hour}
      \correctchoice{Based on computational power}
      \wrongchoice{Manually by developers}
    \end{choices}
  \end{question}
}

\element{class6}{
  \begin{question}{c6q3}
   In blockchain, what role does puzzle difficulty adjustment play in maintaining the network?
    \begin{choices}
      \correctchoice{Enhances security}
      \wrongchoice{Increases transaction speed}
      \wrongchoice{Reduces block size}
      \wrongchoice{Improves decentralization}
    \end{choices}
  \end{question}
}

 
\element{class6}{
  \begin{question}{c6q4}
   Which factor contributes to higher puzzle difficulty in blockchain mining?
    \begin{choices}
      \wrongchoice{Increased network latency}
      \wrongchoice{Higher transaction fees}
      \wrongchoice{Decreased computational power}
      \correctchoice{More miners in the network}
    \end{choices}
  \end{question}
} 


\element{class6}{
  \begin{question}{c6q5}
   What is the downside of Proof of Work in terms of environmental impact?
    \begin{choices}
      \wrongchoice{Low security}
      \correctchoice{High energy consumption}
      \wrongchoice{Lack of scalability}
      \wrongchoice{Slow transaction speed}
    \end{choices}
  \end{question}
}

\element{class6}{
  \begin{question}{c6q6}
  In Proof of Work, how is the difficulty of the cryptographic puzzle adjusted over time?
    \begin{choices}
      \wrongchoice{By the network administrator}
      \correctchoice{Automatically based on the network's hash rate}
      \wrongchoice{Through a voting process}
      \wrongchoice{Randomly}
    \end{choices}
  \end{question}
}

\element{class6}{
  \begin{question}{c6q7}
  How does Proof of Work contribute to the security of a blockchain network?
    \begin{choices}
      \wrongchoice{By encrypting all transactions}
      \correctchoice{Through the competitive nature of mining}
      \wrongchoice{By requiring a central authority's approval}
      \wrongchoice{By implementing smart contracts}
    \end{choices}
  \end{question}
}


\element{class6}{
  \begin{question}{c6q8}
   What role do miners play in the Proof of Work process?
    \begin{choices}
      \wrongchoice{Transaction verification}
      \correctchoice{Block creation}
      \wrongchoice{Network encryption}
      \wrongchoice{Smart contract execution}
    \end{choices}
  \end{question}
}

