\element{class5}{
  \begin{question}{c5q1}
   What is the process of selecting a miner in a blockchain network called?
    \begin{choices}
      \wrongchoice{Mining election}
      \correctchoice{Consensus mechanism}
      \wrongchoice{Miner lottery}
      \wrongchoice{Block validation}
    \end{choices}
  \end{question}
}

\element{class5}{
  \begin{question}{c5q2}
  In Proof of Work (PoW) consensus, how is the miner selected to add a new block to the blockchain?
    \begin{choices}
      \wrongchoice{Random selection}
      \correctchoice{Highest computational power}
      \wrongchoice{Longest chain}
      \wrongchoice{Equal distribution among all nodes}
    \end{choices}
  \end{question}
}

\element{class5}{
  \begin{question}{c5q3}
   What is the primary purpose of the miner election process in a blockchain?
    \begin{choices}
      \wrongchoice{Ensuring fair distribution of rewards}
      \wrongchoice{Enhancing network security}
      \wrongchoice{Speeding up transaction confirmation}
      \correctchoice{All of the above}
    \end{choices}
  \end{question}
}

\element{class5}{
  \begin{question}{c5q4}
   Which consensus algorithm is commonly used in public blockchain networks like Bitcoin?
    \begin{choices}
      \wrongchoice{Proof of Authority (PoA)}
      \wrongchoice{Proof of Stake (PoS)}
      \correctchoice{Proof of Work (PoW)}
      \wrongchoice{Delegated Proof of Stake (DPoS)}
    \end{choices}
  \end{question}
}

\element{class5}{
  \begin{question}{c5q5}
   What is the primary purpose of decentralised consensus in blockchain?
    \begin{choices}
      \wrongchoice{Centralized control}
      \wrongchoice{Increased efficiency}
      \correctchoice{Distributed trust}
      \wrongchoice{Reduced security}
    \end{choices}
  \end{question}
}

\element{class5}{
  \begin{question}{c5q6}
   How is the order of blocks maintained in a blockchain?
    \begin{choices}
      \wrongchoice{Random assignment}
      \wrongchoice{Alphabetical order}
      \correctchoice{Timestamp and cryptographic linkage}
      \wrongchoice{Decentralized voting system}
    \end{choices}
  \end{question}
}


\element{class5}{
  \begin{question}{c5q7}
   Which mathematical puzzle is solved by miners in Nakamoto Consensus to add a block to the blockchain?
    \begin{choices}
      \wrongchoice{Sudoku}
      \wrongchoice{Prime factorization}
      \correctchoice{Hash puzzle}
      \wrongchoice{Differential equations}
    \end{choices}
  \end{question}
}

\element{class5}{
  \begin{question}{c5q8}
   How does a blockchain network ensure that a block is valid before adding it to the chain?
    \begin{choices}
      \wrongchoice{Ethereum}
      \correctchoice{Bitcoin}
      \wrongchoice{Ripple}
      \wrongchoice{Litecoin}
    \end{choices}
  \end{question}
}

